Speed and strength of an epidemic intervention

### 2020-06-17 doc/speedstrength.tex
good night

An epidemic can be described by its \emph{speed} and \emph{strength}.
The speed of an epidemic is characterized by the exponential growth rate $r$, which measures how \emph{fast} an epidemic grows at the population level.
The strength of an epidemic is characterized by the reproductive number \RR, which measures how many new cases are caused by a typical \emph{individual} case.
Knowing the speed and strength of an epidemic allows predictions about the course of the epidemic and the effectiveness of intervention strategies.

>>>>

An epidemic can be described by its \emph{speed} and \emph{strength}.
The speed of an epidemic is characterized by the exponential growth rate $r$, which measures how \emph{fast} an epidemic grows at the population level.
The strength of an epidemic is characterized by the reproductive number \RR, which measures \emph{how many} new cases are caused by a typical individual case.
Knowing the speed and strength of an epidemic allows predictions about the course of the epidemic and the effectiveness of intervention strategies.
